Competence distance

### 2017-05-10 analysis/analysis_competence.Rmd
Create csv with competence indexes

# Read data 
```{r, echo=FALSE}
#machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
# Get name of focal trees
focal_trees <- compete %>% filter(id_focal != 'Fresno') 
focal_trees <- unique(focal_trees$id_focal)

# Empty object to store results 
output<- vector("list", length(focal_trees))

for (i in 1:length(focal_trees)){

@@

  # Compute fixed variables: 
  radius_plot <- 10 # radius plot (10 m)
  sf_plot <- pi * radius_plot^2 # surface plot (m2)
  dnft <- filter(df, sp== 'Focal')$dn # normal diameter of focal tree    
  # ----------

  # Competence indices 
  ## Number of competitors inside plot wihtout focal tree (r = 10)
  n_competitors <- filter(df, sp != 'Focal') %>% count()

  ## Number of competitors with dn_j > dn_i (focal tree)
  n_competitors_hihger <- df %>%
    filter(sp != 'Focal') %>%
    filter(dn > dnft) %>% 
    count()

  ## plot density (tree/plot)
  plot_density <- n_competitors / sf_plot

  ## Stand density (tree / ha) 
  stand_density <- (n_competitors * 10000) / sf_plot

@@

df_indices_plot <- bind_rows(output)

@@

# Export data

>>>>

# Read data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
# 1 Get name of focal trees
focal_trees <- compete %>% filter(id_focal != 'Fresno') 
focal_trees <- unique(focal_trees$id_focal)

# 2 Compute Fixed variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)

# 3 Empty object to store results 
output<- vector("list", length(focal_trees))

# 4 Loop 
for (i in 1:length(focal_trees)){

@@

  # Focal tree
  focal_t <- filter(df, sp== 'Focal') 
  ## Normal diameter of focal tree
  dnft <- focal_t$dn

  # Competence indices 
  ## Number of competitors inside plot wihtout focal tree (r = 10)
  n_competitors <- filter(df, sp != 'Focal') %>% count() %>% transmute(n_competitors = n)

  ## Number of competitors with dn_j > dn_i (focal tree)
  n_competitors_hihger <- df %>%
    filter(sp != 'Focal') %>%
    filter(dn > dnft) %>% 
    count() %>% 
    transmute(n_competitors_hihger = n)

  ## plot density (tree/plot)
  plot_density <- n_competitors$n_competitors / sf_plot

  ## Stand density (tree / ha) 
  stand_density <- (n_competitors$n_competitors * 10000) / sf_plot

@@

# df_indices_plot <- bind_rows(output)
# As the output is a nested list I used this solution (http://stackoverflow.com/questions/27930883/converting-elements-in-a-nested-list-to-dataframe) to convert to a dataframe

df_indices_plot <- bind_rows(lapply(output, as.data.frame.list, stringsAsFactors=FALSE))

@@

# Export data 
write.csv(df_indices_plot, file=paste(di, "data/competence/competence_indexes.csv", sep=""), row.names = FALSE)
```
